\documentclass[parskip=full]{scrartcl}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[german]{babel}
\usepackage{hyperref}
\usepackage{enumitem}

\title{Project Ethos : Spezifications}
\author{NouCake}
\setlist[itemize]{noitemsep}

\begin{document}

\maketitle

\section{What is Ethos?}
Project Ethos is a fast-paced multyplayer game for up to 4 player. The player will battle each other for a final winner.

\section{Main Target}
The main target is to create a shortwhile and fun experience for the player. Its not to ment to be competitive.

\section{User}
A fun game for all Users.

Targetgroup: User of all ages.\newline 
Platform: Desktop-Pc, Mobile Devices.

\newpage
\section{Functional Conditions}
\subsection{Server}
A Server is a Object that manages all connections between Server and Client.
\begin{itemize}
	\item managing clients
	\item managing connections
	\item passes relevant data to GameServer
\end{itemize}

\subsection{GameServer}
Manages relevant data for the game.
\begin{itemize}
	\item managing entitys
	\item managing Physics
	\item managing Input
	\item responsible for provoding all neccessary information for entitys
	\item updates entitys
	\item updates physics
	\item updates input
	\item validating incoming packages
\end{itemize}

\subsection{Physics}
Managing all physics relevant data and responsible for all physical calculations
\begin{itemize}
	\item calculates all physics
	\item calculates collision and informs colliding entitys
	\item does not save any data about entitys
\end{itemize}
\section{Ablauf} %Maybe Flow is a good name?
User starts game, everything is nice. Like Bob Ross did it.

\subsection{Server}
\begin{itemize}
	\item Server gets booted
	\item Server waits for enough player to connect
	\item as soon as a lobby gets started Server creates a GameServer
	\item GameServers starts and loads a map
	\item GameServer loads UiOall connected player into map
\end{itemize}


\subsection{Client}
\begin{itemize}
	\item User starts Client
	\item Client displays a connection screen
	\item Client connects to Server
	\item After successful connection Client show GameState
\end{itemize}

\subsubsection{Timing}
Server starts and inits gameserver
(t=0)gameserver sets the time=0 at init and updates it 
(a function getTime that calculates current time)\newline
(t=1200)client logs in and requests welcome package\newline
(t=1200)server send current time(t=1200) to client (with 30ms delay)\newline
(t=1230)client receives currentTime(1200) and saves it for server communication (pos 1)\newline
(t=1300)client updates its state, loggs his old state(t=12700, pos1) and sends input data to server(time = 1270)\newline
(t=1300)server updates state and sends pos data to client(t=1300, pos = 1)\newline
(t=1330)server receives client package and sets input of player(t=1270)\newline
(t=1330)(cT=1300)client receives pos data from server(t=1300, pos 1) and compares it to logged data(t=1270, pos=1)




\subsubsection{Recieving Data}
The client receives data in realtime. This data contains:
EntityData
The client updates its state with the entity data.
data for the player that belogns to the client will checks if the 

\end{document}
